Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-27 paper.tex
did some edtis on lemma 2-4

\begin{lemma}
$P(A_t\neq B(\theta_t)|t\in [t_n, t_{n+1}-1],\theta_t\cdot(u_{B(\theta_t)}-u_{\hat{B}(\theta_t)})\geq 2m\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{proof}[Proof of Lemma~\ref{round:prob}]
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that a myopic action can incur regret is bounded by
\begin{align}
&P(\text{myopic action incurs regret})\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we need to use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,t)}=\sum_{k\in\tau_{i,t}}\frac{\epsilon_{k}}{\sqrt{2}\sigma}=\frac{1}{\sqrt{2}\sigma}\sum_{k\in\tau_{i,t}}\epsilon_{k}. \nonumber
\end{align}

@@

Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,t)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+bN(i,t)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right) \nonumber \\
=&2P\left(S_{N(i,t)}>\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
\leq & 2P\left(S_{N(i,t)}> \sqrt{0.6 N_{i,t}\log(\log_{1.1}(N(i,t))+1)+b N(i,t)}\right) \nonumber \\
\leq & 24\exp( -1.8b) \nonumber \\
= & 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right)  \nonumber \\
=& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

@@

\begin{proof}
Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Define
\begin{align}
W^{'}[l] = \{\omega_t:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,j\}\nonumber
\end{align}
where $g(n,l)$ is a function which we will define later. Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$. We call $W[l]$ the $l^{th}$ envelope.

>>>>

\begin{lemma}
Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, then for all the agents whose utility difference between their best and second best arm is at least $2m\lambda$, we have $P(A_{\tau}\neq B(\theta_{\tau}))\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

\begin{proof}[Proof of Lemma~\ref{round:prob}]
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, for all the agents whose utility difference between their best and second best arm is greater than $2m\lambda$, we have
\begin{align}
&P(A_{\tau}\neq B(\theta_{\tau}))\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we need to use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{\sqrt{2}\sigma}. \nonumber
\end{align}

@@

Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,\tau)} \nonumber \\
\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda) \nonumber \\
=&2P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
\leq & 2P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right) \nonumber \\
\leq & 24\exp( -1.8b) \nonumber \\
= & 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda)  \nonumber \\
\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

@@

\begin{proof}
Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$. Define
\begin{align}
W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
\end{align}
where $g(n,l)$ is a function which we will define later. Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$. We call $W[l]$ the $l^{th}$ envelope.
